\documentclass[11pt]{article}

% helpful packages
\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{enumitem}

% global formatting tweaks
\pagestyle{empty}
\geometry{margin=0.5in}
\setlength\parindent{9pt}
\setlist{nosep}
\renewcommand\labelitemi{--}

% new commands!
\newcommand{\name}[1]{\begin{center}\section*{\huge #1}\end{center}}
\newcommand{\topinfo}[1]{\begin{center}\vspace{-0.2cm}#1\vspace{-0.2cm}\end{center}}
\newcommand{\resumesection}[1]{\vspace{-0.2cm}\section*{#1}\vspace{-0.2cm}\hrule\vspace{0.2cm}}

\begin{document}

\name{Adam Jean-Laurent}
\topinfo{github.com/adamjeanlaurent}
\topinfo{linkedin.com/in/adam-jean-laurent}
\topinfo{adamjeanlaurent@gmail.com}
\topinfo{401-474-7862}

\resumesection{Education}

\textbf{University Of Rhode Island}, Kingston, RI \hfill May 2021 (Expected)
\begin{itemize}
	\item Bachelor of Arts (BA) in Computer Science, 3.43/4.0 GPA.
	\item Coursework includes Data Structures \& Algorithms, Object-Oriented Programming, Math Tools For Computing, Software Engineering, Web Design, Calculus, Statistics, and Fundamentals Of Programming Languages. 
\end{itemize}

\resumesection{Experience}

\textbf{Microsoft}, New Technologist Intern \hfill June 2019--Present
\begin{itemize}
	\item Starting June 24th
\end{itemize}

\textbf{University Of Rhode Island}, IT Consultant \hfill September 2018--Present
\begin{itemize}
	\item Provide professional computing services to URI community such as troubleshooting, reformatting, Ethernet port-teching, and other software/hardware issues.
	\item Use verbal communication over the phone, and written communication when writing trouble tickets and emails.
\end{itemize}

\resumesection{Projects}

\textbf{YouTube Sync}, https://github.com/adamjeanlaurent/YouTube-Sync  
\begin{itemize}
	\item Built web application that allows users to synchronize their YouTube video even when pausing, playing, and skipping.
	\item Implemented websockets on to express web server using socket.io.
	\item Used the YouTube iFrame Player API to create custom YouTube player capable of intercating with a websocket server.
	\item Used HTML/CSS, JavaScript, Node.js, and Git.
\end{itemize}

\textbf{Pomodoro Study}, https://github.com/adamjeanlaurent/Pomodoro-Study
\begin{itemize}
	\item Built a CRUD web application to help users practice the Pomodoro study technique.
	\item  Built backend authorization system that allowed users to register/login, have cookies/sessions.
	\item Used CanvasJS to display user study data visually.
	\item Used HTML/CSS, JavaScript, Node.js, MongoDB, Bootstrap, and Git.
\end{itemize}

\resumesection{Skills}

\textbf{Programming Languages}
\begin{itemize}
	\item (Proficient) JavaScript, HTML, CSS, C, C++, (Intermediate) Python 
\end{itemize}

\textbf{Frameworks}
\begin{itemize}
	\item jQuery, Node.js, Express.js, Bootstrap
\end{itemize}

\textbf{Tools/Databases}
\begin{itemize}
	\item Visual Studio, APIs, Bash, Git, MySQL, MongoDB, \LaTeX
\end{itemize}

\resumesection{Activities}

\textbf{Academic Excellence Chair}, National Society Of Black Engineers \hfill April 2019--Present
\begin{itemize}
	\item Promote attendance and participation in NSBE meeting and activities.
	\item Organize tutoring, and refer members to academic and career counseling.
	\item Plan professional development and hands on workshop events.
\end{itemize}

\textbf{Telecommunications Committee}, National Society Of Black Engineers \hfill April 2019--Present
\begin{itemize}
	\item Work on a small team to design and build URI NSBE's website.
\end{itemize}

\end{document}
